State of the Art in Scientific Workflow Systems

### 2014-05-28 paper.tex
wings desc

%
\paragraph{Pegasus/DAX} Pegasus \cite{deelman-peg} is an SWE that is
well-suited to generate and execute large workflows from abstract DAGs
describing dataflow.  Abstract description of a DAG is done via an XML-based
language called DAX. The concrete expression takes into account the properties
of application task requirements and underlying distributed compute resources.
The main advantage of such approach is that a single abstract workflow
description can be mapped to multiple execution environments based on
requirements. DAX describes the logical workflow components, their inputs and
outputs and their links and dependencies in a Pegasus workflow. These kind of
workflows have been shown to enact optimally using Pegasus' dynamic task,
memory and disk management techniques. For instance, for massively parallel
task scheduling, Pegasus provides a task clustering technique that groups
parallel jobs based on fixed parameters such as number of groups. Additionally,
a manager buffers and maintains a fix-sized window of executable tasks before
accepting new tasks.

@@

\paragraph{Wings/--} The Workflow instance generation and specialization
(Wings) provides automatic workflow validation and generation based on
high-level workflow templates~\cite{wings2013}. The system receives high-level
workflow specification in the form of Pegasus/DAX workflows and generates
concrete executable workflows. It generates workflows by selecting components,
data sets, and parameters in three stages while eliminating candidates that are
not viable.

>>>>

%
\paragraph{Pegasus/DAX} Pegasus \cite{deelman-peg} is an SWE
well-suited to generate and execute large workflows from abstract DAGs
describing dataflow among interdependent tasks. Abstract description of a DAG
is done via an XML-based language called DAX. The concrete expression takes
into account the properties of application task requirements and underlying
distributed compute resources.  The main advantage of such approach is that a
single abstract workflow description can be mapped to multiple execution
environments based on requirements. DAX describes the logical workflow
components, their inputs and outputs and their links and dependencies in a
Pegasus workflow. These kind of workflows have been shown to enact optimally
using Pegasus' dynamic task, memory and disk management techniques. For
instance, for massively parallel task scheduling, Pegasus provides a task
clustering technique that groups parallel jobs based on fixed parameters such
as number of groups. Additionally, a manager buffers and maintains a fix-sized
window of executable tasks before accepting new tasks.

@@

\paragraph{Wings/--} The Workflow instance generation and specialization
(Wings) provides automatic workflow validation and generation based on
high-level workflow templates~\cite{wings2013}. The system receives high-level
workflow specification in the form of Pegasus/DAX workflows and validates them
for correct coordination based on data and resource constraints. It generates
workflows by selecting components, data sets, and parameters in three stages
while eliminating candidates that are not viable. This approach is useful in
the context of desiging complex computational experiments by domain scientists
in that it eases the process of workflow level debugging.
